---
title: "Analysis_sockult"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
library(tidyverse)
```

#DATA CLEANING

#Importing dataframe and extracting all participants who finished as well as offer and response columns
```{r warning=FALSE, include=FALSE}

wide<-read_csv("data/all_apps_wide_2021-05-05-2.csv") #loading the wide dataframe with all data from oTree

df_wide<-filter(wide, wide$participant._current_page_name == "ThankYou") #filtering all participants who did not finish the experiment away. The last page in the experiment is called "ThankYou".


Columns_offers<-grep(pattern="\\.Offer$", #Filtering the df_wide dataframe for all columns where participants give offers
    x=colnames(df_wide))

Columns_responds<-grep(pattern="\\.bot_side$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

OfferDf<- df_wide[, colnames(df_wide)[Columns_offers]] #A df with data from offers

ResponseDf<-df_wide[, colnames(df_wide)[Columns_responds]]  #A df with bot response
```


#offer df
```{r include=FALSE}
#Extracting participant code, age and gender and adding them to the OfferDf
OfferDf["ParticipantCode"] <- df_wide$participant.code 
OfferDf["Age"] <- df_wide$Consentform.1.player.Age
OfferDf["Gender"] <- df_wide$Consentform.1.player.Gender

#relocating to the beginning of the dataframe
OfferDf <- OfferDf %>% 
  relocate(ParticipantCode, Age, Gender, .before =ultimatumn_anonym.1.player.Offer)

#removing 
colnames(OfferDf) <- sub(".player.Offer", "", colnames(OfferDf))
colnames(OfferDf) <- sub("Persona", "P", colnames(OfferDf))
colnames(OfferDf) <- sub("ultimatumn_anonym", "An", colnames(OfferDf))
colnames(OfferDf) <- sub("An.1", "An1", colnames(OfferDf))
colnames(OfferDf) <- sub("An.2", "An1.2", colnames(OfferDf))
colnames(OfferDf) <- sub("An.3", "An1.3", colnames(OfferDf))
colnames(OfferDf) <- sub("An.4", "An1.4", colnames(OfferDf))
colnames(OfferDf) <- sub("An.5", "An1.5", colnames(OfferDf))
colnames(OfferDf) <- sub("An.6", "An1.6", colnames(OfferDf))
colnames(OfferDf) <- sub("An.7", "An1.7", colnames(OfferDf))
colnames(OfferDf) <- sub("An.8", "An1.8", colnames(OfferDf))
colnames(OfferDf) <- sub("An.9", "An1.9", colnames(OfferDf))
colnames(OfferDf) <- sub("An.10", "An10", colnames(OfferDf))
```




#response df
```{r include=FALSE}
ResponseDf["ParticipantCode"] <- df_wide$participant.code 
ResponseDf["Age"] <- df_wide$Consentform.1.player.Age
ResponseDf["Gender"] <- df_wide$Consentform.1.player.Gender

colnames(ResponseDf) <- sub("ultimatumn_anonym", "An", colnames(ResponseDf))
colnames(ResponseDf) <- sub("player.bot_side", "Response", colnames(ResponseDf))
colnames(ResponseDf) <- sub("ultimatumn_anonym", "An", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.1", "An1", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.2", "An1.2", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.3", "An1.3", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.4", "An1.4", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.5", "An1.5", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.6", "An1.6", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.7", "An1.7", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.8", "An1.8", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.9", "An1.9", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.10", "An10", colnames(ResponseDf))
colnames(ResponseDf) <- sub("Persona", "P", colnames(ResponseDf))

ResponseDf <- ResponseDf %>% 
  relocate(ParticipantCode, Age, Gender, .before =An1.Response)
```



#Creating dataframe with responses and offers 
```{r include = FALSE}
#Combining responsedf and offerdf
Combined<-cbind(ResponseDf, OfferDf)

#including participants

Combined["ParticipantCode"] <- df_wide$participant.code 
Combined["Age"] <- df_wide$Consentform.1.player.Age
Combined["Gender"] <- df_wide$Consentform.1.player.Gende

#removing 
colnames(Combined ) <- sub(".player.Offer", "", colnames(Combined ))
colnames(Combined ) <- sub("Persona", "P", colnames(Combined ))
colnames(Combined) <- sub("player.bot_side", "Response", colnames(Combined))
colnames(Combined ) <- sub("ultimatumn_anonym", "An", colnames(Combined ))
colnames(Combined ) <- sub("An.1", "An1", colnames(Combined ))
colnames(Combined ) <- sub("An.2", "An1.2", colnames(Combined ))
colnames(Combined ) <- sub("An.3", "An1.3", colnames(Combined ))
colnames(Combined ) <- sub("An.4", "An1.4", colnames(Combined ))
colnames(Combined ) <- sub("An.5", "An1.5", colnames(Combined ))
colnames(Combined ) <- sub("An.6", "An1.6", colnames(Combined ))
colnames(Combined ) <- sub("An.7", "An1.7", colnames(Combined ))
colnames(Combined ) <- sub("An.8", "An1.8", colnames(Combined ))
colnames(Combined ) <- sub("An.9", "An1.9", colnames(Combined ))
colnames(Combined ) <- sub("An.10", "An10", colnames(Combined ))

Combined <- Combined %>% 
  relocate(Gender, .before =An1.Response)

```




#From wide to long format
```{r warning=FALSE, include=FALSE}
#from wide to long format for the Offer only df
df_long<-reshape(OfferDf, 
        direction = "long",
        varying = list(names(OfferDf)[4:83]),
        v.names = "Offer",
        idvar = c("ParticipantCode", "Age", "Gender"),
        timevar = "Round",
        times = c(names(OfferDf)[4:83]))

#Using a combined dataframe to convert response to long format
df_respons_long<-reshape(Combined, 
        direction = "long",
        varying = list(names(Combined)[4:83]),
        v.names = "Response",
        idvar =  "ParticipantCode",
        timevar = "Round",
        times = c(names(Combined)[4:83]))
```


#Creating Is_anonymous, OtherPlayer, PrevOffer, PrevResonse, centered_PrevOffer
```{r warning=FALSE}

df_long["Response"]<- df_respons_long$Response
df_long["Is_anonymous"] <- ifelse(grepl("An",df_long$Round),'1','0')

#df_long["OtherPlayer"] <- ifelse(grepl("An.",df_long$Round),str_extract(df_long$Round, "\\d"),str_extract(df_long$Round, "\\d"))

#class(df_long$OtherPlayer)

#df_long$OtherPlayer<-as.factor(df_long$OtherPlayer)


x<-rep(c(1,2,3,4,5,6,7,8),each=10)

df_long <- df_long %>% 
  group_by(ParticipantCode) %>% 
  mutate(Other = x)


pacman::p_load(tidyverse, ggpubr, groupdata2, lme4, lmerTest)


df_long["Response"]<- df_respons_long$Response#lagging response and offer
df_long <- df_long %>% 
  group_by(ParticipantCode, Other) %>% 
  mutate(PrevOffer = lag(Offer),
         PrevResponse =lag(Response))

#adding centered previous offer
df_long <- df_long %>% 
  group_by(ParticipantCode, Other) %>% 
  mutate(centered_PrevOffer = ( PrevOffer - 50))

```


#Analysis
```{r}

```




#Semantic part, for participants:
```{r}

#df_wide$description.1.player.about_you
#about_you<-grep(pattern="\\.about_you$", #Filtering the df_wide dataframe for all columns where bot responds
  #  x=colnames(df_wide))
#Descriptions<- df_wide[, colnames(df_wide)[about_you]] 

#Descriptions["ParticipantCode"] <- df_wide$participant.code   

```


#Making Persona dataframes with one word in each row
```{r}
library(dplyr)
library(tidytext)
Persona_1<-c('I am a 24 year old woman and I study international business communication in Spanish on 5th semester at bachelor’s level. In my spare time I’m active in a political youth party and I like going on long walks with my friends from my studies and the party. During corona I have been baking sourdough bread and started going for walks.')

Persona_2<- c('Work as a personal consultant in Danske bank guiding clients with investments. When I’m off work, I am together with my fiancé and kids. I golf and ride mountain bike with my coworkers in the weekends/off-work days')

Persona_3<-c('My name is Camilla and I’m 19 years old. Im in 3.G in Gymnasium and become a student in June. After the summer i want to study a bachelor in law at Aalborg university and move there with my two friends from my gymnasium. In my spare time i read a lot and watch some Netflix shows.')

Persona_4<-c('I am 23 years old and work part time in Bilka in the garden department. I like taking rides on my motorcycle. I enjoy gardening, cooking and spending time with my friends and play with my cat. I am trying to get a job as an environmental technologist. I am not doing much during these times, looking forward to an open world again so I can travel.')

Persona_5<-c('I’m 21 years old and a student.I study datascience and I have a student-job at a printer firm. In my free time I play piano, paint and read books. I also enjoy watching YouTube and I spend way too much time on Twitter')

Persona_1<-data.frame(Persona_1) %>% unnest_tokens(word, Persona_1)%>%rename(Persona_1 = word)
  
Persona_2<-data.frame(Persona_2) %>% unnest_tokens(word, Persona_2)%>% rename(Persona_2 = word)

Persona_3<-data.frame(Persona_3) %>% unnest_tokens(word, Persona_3) %>% rename(Persona_3 = word)

Persona_4<-data.frame(Persona_4) %>% unnest_tokens(word, Persona_4) %>% rename(Persona_4 = word)

Persona_5<-data.frame(Persona_5) %>% unnest_tokens(word, Persona_5)%>% rename(Persona_5 = word)


#install.packages("tidytext")

```

to do:
Semantic analysis:
- Merge persona with 300 semantic dimensions and taking mean for each dimension pr. persona
- Do the same for each participant
- cosine similarity between them

Bayesian analysis:
- Find meta analytic prior and see what others do...

models:
i) comparison of anonym vs. non-anonym (gender as random effect and participant ID as random intercept)

ii) comparison between personas (predict offer by cosine similarity between persona and person)

iii) maybe model offer over time (response interacting with centered offer)







